Exception Handling Bug Hazards in Android

### 2015-10-12 SPRINGER_JOURNAL/msr_journal.tex
addressing Christpph and Arie's suggestions

The remainder of this paper is organized as follows. 
Section~\ref{sec:back} provides the necessary
background on the Android platform and the Java exception model. 
Section~\ref{sec:study} presents the study design. 
Section~\ref{sec:exceptionminer} describes the ExceptionMiner tool we developed to conduct our study.
Section~\ref{sec:result} reports the findings of our study.
Section~\ref{sec:disc} provides a discussion of the wider implications of our results,
 presents the threats to validity associated with the mining study and discusses the limitations
of the survey-based study. 
Finally Section~\ref{sec:rele} describes related work, 
and Section~\ref{sec:conc} concludes the paper and outlines
directions for future work.
\section{Background}
\label{sec:back}

@@

java.lang.NullPointerException	&	332	&	51.96\%	&	1664	&	27.71\%	&	525	&	20	&	836	&	280	\\
java.lang.IllegalStateException	&	120	&	18.78\%	&	278	&	4.63\%	&	185	&	31	&	41	&	39	\\
java.lang.IllegalArgumentException	&	142	&	22.22\%	&	353	&	5.88\%	&	195	&	12	&	95	&	44	\\
java.lang.RuntimeException	&	122	&	19.09\%	&	319	&	5.31\%	&	203	&	2	&	64	&	51	\\
java.lang.OutOfMemoryError	&	78	&	12.21\%	&	237	&	3.95\%	&	141	&	16	&	35	&	34	\\
java.lang.NoClassDefFoundError	&	67	&	10.49\%	&	94	&	1.57\%	&	10	&	0	&	46	&	37	\\
java.lang.ClassCastException	&	64	&	10.02\%	&	130	&	2.16\%	&	55	&	0	&	55	&	20	\\
java.lang.IndexOutOfBoundsException	&	62	&	9.70\%	&	166	&	2.76\%	&	53	&	0	&	93	&	18	\\
java.lang.NoSuchMethodError	&	54	&	8.45\%	&	80	&	1.33\%	&	10	&	0	&	56	&	14	\\
java.util.ConcurrentModificationException	&	43	&	6.73\%	&	65	&	1.08\%	&	5	&	0	&	46	&	13	\\
    \hline
  \end{tabular}
\caption{Root Exceptions occurrences and popularity in repositories hosted on Google Code (GC) and GitHub(GH).}
\label{tab:topten}
\end{table*}

@@

 In previous work~\cite{coelhoetal15}, we mined exception stack traces available in issues reported for several Android projects hosted on GitHub and Google Code. To ensure that our sample consists of repositories that were real Android apps, we had to inspect every project site and discard toy-programs and non-Android repositories. For each repository, we extract the developers whose emails are registered. We emailed the 1,824 developers and received 71 valid answers. The majority of our respondents have more than 2 years of Java development experience (87.3\%) and  considerable experience in Android development (more than 1 year)  (85.9\%) -- see Figure~\ref{fig:devexpertise}.

@@

\section{Replication Package}
All the data used in the mining study and in the survey-based study is publicly available at the ExceptionMiner tool website hosted on GitHub\footnote{\url{https://github.com/souzacoelho/exceptionminer}}.
Specifically we provide: (i) all issues related to Android projects found
on GitHub and Google Code used in this study; (ii) all stack traces extracted
from issues; (iii) the results of manual inspection steps; (iv) the
ExceptionMiner tool we developed to support stack trace extraction and distilling; (v) the survey questions; and (iv) the survey responses and summary.

@@

%\noindent

>>>>

%Section~\ref{sec:exceptionminer} 
%Section~\ref{sec:result}

The remainder of this paper is organized as follows. 
Section~\ref{sec:back} provides the necessary
background on the Android platform and the Java exception model. 
Section~\ref{sec:study} presents the mining study design, describes the ExceptionMiner tool 
we developed to conduct our study, and reports the study results.
Section~\ref{sec:dev} details the exploratory survey.
Section~\ref{sec:disc} provides a discussion of the wider implications of our results,
 presents the threats to validity associated with the mining study and discusses the limitations
of the survey-based study, and points to the replication. 
Finally Section~\ref{sec:rele} describes related work, 
and Section~\ref{sec:conc} concludes the paper and outlines
directions for future work.
\section{Background}
\label{sec:back}

@@

java.lang.NullPointerException	&	332	&	51.96\%	&	1664	&	27.71\%	&	525	&	20	&	836	&	280	\\
java.lang.IllegalStateException	&	120	&	18.78\%	&	278	&	4.63\%	&	185	&	31	&	41	&	39	\\
java.lang.IllegalArgumentException	&	142	&	22.22\%	&	353	&	5.88\%	&	195	&	12	&	95	&	44	\\
java.lang.RuntimeException	&	122	&	19.09\%	&	319	&	5.31\%	&	203	&	2	&	64	&	51	\\
java.lang.OutOfMemoryError	&	78	&	12.21\%	&	237	&	3.95\%	&	141	&	16	&	35	&	34	\\
java.lang.NoClassDefFoundError	&	67	&	10.49\%	&	94	&	1.57\%	&	10	&	0	&	46	&	37	\\
java.lang.ClassCastException	&	64	&	10.02\%	&	130	&	2.16\%	&	55	&	0	&	55	&	20	\\
java.lang.IndexOutOfBoundsException	&	62	&	9.70\%	&	166	&	2.76\%	&	53	&	0	&	93	&	18	\\
java.lang.NoSuchMethodError	&	54	&	8.45\%	&	80	&	1.33\%	&	10	&	0	&	56	&	14	\\
java.util.ConcurrentModificationException	&	43	&	6.73\%	&	65	&	1.08\%	&	5	&	0	&	46	&	13	\\
    \hline
  \end{tabular}
\caption{Root Exceptions occurrences and popularity in analyzed repositories.}
\label{tab:topten}
\end{table*}

@@

 In previous work~\cite{coelhoetal15}, we mined exception stack traces available in issues reported for several Android projects hosted on GitHub and Google Code. To ensure that our sample consists of repositories that were real Android apps, we had to inspect every project site and discard toy-programs and non-Android repositories. For each repository, we extract the developers whose emails are registered. We emailed the 1,824 developers and received 71 valid answers. The majority of our respondents have more than 2 years of Java development experience (87.3\%) and of Android development (85.9\%) -- see Figure~\ref{fig:devexpertise}.

@@

@@

\subsection{Replication Package}
All the data used in the mining study and in the survey-based study is publicly 
available at the ExceptionMiner tool website hosted on GitHub\footnote{\url{https://github.com/souzacoelho/exceptionminer}}.
Specifically we provide: (i) all issues related to Android projects found
on GitHub and Google Code used in this study; (ii) all stack traces extracted
from issues; (iii) the results of manual inspection steps; (iv) the
ExceptionMiner tool we developed to support stack trace extraction and distilling; 
(v) the survey questions; and (iv) the survey responses and summary.
